The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-04-09 manuscript/manuscript.qmd
fixed citation typo

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*). An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a]. China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a recent global wave of legal restrictions on INGOs. As an authoritarian jurisdiction with a growing nonprofit sector, the Chinese model of implementing restrictive laws for INGOs has great implications for scholarly understanding of the dynamics of how such laws are used as policy tools to harness INGOs in practice. The purpose of this study is to empirically examine how the ONGO Law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we intent to inquire into a more comprehensive and data-based picture of the operational space for INGOs. It will also test out the evolving theory of the "closing space" or "changing space" for INGOs hold true in a representative empirical setting of the mainland China.

@@

Also, [@Plantan2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."

@@

The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss2022; @Carothers:2016].  Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies [@Jia2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

>>>>

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss:2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*). An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a]. China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a recent global wave of legal restrictions on INGOs. As an authoritarian jurisdiction with a growing nonprofit sector, the Chinese model of implementing restrictive laws for INGOs has great implications for scholarly understanding of the dynamics of how such laws are used as policy tools to harness INGOs in practice. The purpose of this study is to empirically examine how the ONGO Law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we intent to inquire into a more comprehensive and data-based picture of the operational space for INGOs. It will also test out the evolving theory of the "closing space" or "changing space" for INGOs hold true in a representative empirical setting of the mainland China.

@@

Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."

@@

The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss:2022; @Carothers:2016].  Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies [@Jia:2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.
